---
title: "Project"
format: html
editor: visual
---

```{r include = FALSE}
library(tidyquant)
library(tidyverse)
library(lubridate)
```

### Create Dataframes for the portfolio's of 5(or so) best stocks for the different years

```{r}
wts3 = rep(1/3, 3)
wts4 = rep(.25, 4)
wts5 = rep(.2, 5)
  ## 2009 Portfolio
stocks_2009_v <- c("XL", "THC", "AMD", "F", "GNW")
df_stocks_2009 <- stocks_2009_v %>% 
  tq_get(get = "stock.prices", from = "2010-01-01", to = "2014-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts4,
               col_rename = "Return")
  ## 2010 Portfolio
stocks_2010_v <- c("CMI", "AKAM", "CRM", "BKNG", "CTBB")
df_stocks_2010 <- stocks_2010_v %>% 
  tq_get(get = "stock.prices", from = "2011-01-01", to = "2015-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts4,
               col_rename = "Return")
  ## 2011 Portfolio
stocks_2011_v <- c("CTRA", "EP-C", "MA", "HUM", "OKE")
df_stocks_2011 <- stocks_2011_v %>% 
  tq_get(get = "stock.prices", from = "2012-01-01", to = "2016-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts4,
               col_rename = "Return")
  ## 2012 Portfolio
stocks_2012_v <- c("SHLD", "BAC", "NFLX", "WHR", "FII")
df_stocks_2012 <- stocks_2012_v %>% 
  tq_get(get = "stock.prices", from = "2013-01-01", to = "2017-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts3,
               col_rename = "Return")
  ## 2013 Portfolio
stocks_2013_v <- c("NFLX", "BBY", "MU", "DAL", "PBI")
df_stocks_2013 <- stocks_2013_v %>% 
  tq_get(get = "stock.prices", from = "2014-01-01", to = "2018-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts5,
               col_rename = "Return")
  ## 2014 Portfolio
stocks_2014_v <- c("LUV", "EA", "EW", "AVGO", "AGN")
df_stocks_2014 <- stocks_2014_v %>% 
  tq_get(get = "stock.prices", from = "2015-01-01", to = "2019-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts4,
               col_rename = "Return")
  ## 2015 Portfolio
stocks_2015_v <- c("NFLX", "AMZN", "ATVI", "NVDA", "HRL")
df_stocks_2015 <- stocks_2015_v %>% 
  tq_get(get = "stock.prices", from = "2016-01-01", to = "2020-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts4,
               col_rename = "Return")
  ## 2016 Portfolio
stocks_2016_v <- c("NVDA", "OKE", "FCX", "NEM", "SEP")
df_stocks_2016 <- stocks_2016_v %>% 
  tq_get(get = "stock.prices", from = "2017-01-01", to = "2021-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts5,
               col_rename = "Return")  %>% 
  filter(date != "2018-12-17")
  ## 2017 Portfolio
stocks_2017_v <- c("ALGN", "NRG", "FSLR", "VRTX", "MU")
df_stocks_2017 <- stocks_2017_v %>% 
  tq_get(get = "stock.prices", from = "2018-01-01", to = "2022-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts5,
               col_rename = "Return")
  ## 2018 Portfolio
stocks_2018_v <- c("AMD", "ABMD", "FTNT", "TRIP", "RHT")
df_stocks_2018 <- stocks_2018_v %>% 
  tq_get(get = "stock.prices", from = "2019-01-01", to = "2023-12-31") %>% 
  group_by(symbol) %>% 
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return") %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Return,
               weights = wts4,
               col_rename = "Return") %>% 
  filter(date != "2022-12-23")
```

### Create the S&P 500 dataframes for each year

```{r}
  ##SP500 2009
df_SP500_2009 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2010-01-01",
                        to = "2014-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
  ##SP500 2010
df_SP500_2010 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2011-01-01",
                        to = "2015-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
  ##SP500 2011
df_SP500_2011 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2012-01-01",
                        to = "2016-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
  ##SP500 2012
df_SP500_2012 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2013-01-01",
                        to = "2017-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
  ##SP500 2013
df_SP500_2013 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2014-01-01",
                        to = "2018-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
  ##SP500 2014
df_SP500_2014 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2015-01-01",
                        to = "2019-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
  ##SP500 2015
df_SP500_2015 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2016-01-01",
                        to = "2020-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
  ##SP500 2016
df_SP500_2016 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2017-01-01",
                        to = "2021-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
  ##SP500 2017
df_SP500_2017 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2018-01-01",
                        to = "2022-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
  ##SP500 2018
df_SP500_2018 <- tq_get(x = "SPY",
                        get = "stock.prices",
                        from = "2019-01-01",
                        to = "2023-12-31") %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly",
               col_rename = "Return")
```

### Join each year into its own distinct dataframe with a S&P 500 column and a portfolio column

```{r }
  ##2009
df_2009 <- df_SP500_2009 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2009$Return,
         date = ymd(date),
         year_inception = '2009')
  ##2010
df_2010 <- df_SP500_2010 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2010$Return,
         date = ymd(date),
         year_inception = '2010')
  ##2011
df_2011 <- df_SP500_2011 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2011$Return,
         date = ymd(date),
         year_inception = '2011')
  ##2012
df_2012 <- df_SP500_2012 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2012$Return,
         date = ymd(date),
         year_inception = '2012')
  ##2013
df_2013 <- df_SP500_2013 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2013$Return,
         date = ymd(date),
         year_inception = '2013')
  ##2014
df_2014 <- df_SP500_2014 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2014$Return,
         date = ymd(date),
         year_inception = '2014')
  ##2015
df_2015 <- df_SP500_2015 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2015$Return,
         date = ymd(date),
         year_inception = '2015')
  ##2016
df_2016 <- df_SP500_2016 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2016$Return,
         date = ymd(date),
         year_inception = '2016')
  ##2017
df_2017 <- df_SP500_2017 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2017$Return,
         date = ymd(date),
         year_inception = '2017')
  ##2018
df_2018 <- df_SP500_2018 %>% 
  rename("SP500_Return" = "Return") %>% 
  mutate(portfolio = df_stocks_2018$Return,
         date = ymd(date),
         year_inception = '2018')
```

### Create a total returns dataframe for funzies and graphing

```{r}
df_total_returns <- rbind(df_2009, df_2010, df_2011, df_2012, df_2013, df_2014, df_2015, df_2016, df_2017, df_2018)
```

### Create a new dataframe that has columns for the growth of x number of dollars invested in each our picked portfolio and the SP500 and a collumn "Years since inception" which is the years since the portfolio was formed

```{r}
df_total_growth <- df_total_returns %>% 
  group_by(year_inception) %>% 
  mutate(SP500_Cum = cumprod(1 + SP500_Return),
         RAND_Cum = cumprod(1 + portfolio))

df_total_growth <- df_total_growth %>% 
  ungroup() %>% 
  mutate(years_since_inception = year(df_total_growth$date) - as.numeric(df_total_growth$year_inception))

```

### Growth of investment over time plot, faceted by inveption year(year of top 5 stocks, pushed out 5 years)

```{r}
colors <- c("SP500" = "blue", "Created Portfolio" = "red")
df_total_growth %>%
  ggplot(aes(x = years_since_inception)) +
  geom_line(aes(y = SP500_Cum * 5000, color = "S&P 500"), linetype = "solid") +
  geom_line(aes(y = RAND_Cum * 5000, color = "Created Portfolio"), linetype = "solid") +
  facet_wrap(vars(year_inception)) +
  labs(title = "Portfolio Growth Comparison",
       subtitle = "Investment Value",
       y = NULL,
       x = "Years After Start Date",
       color = "Legend") +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5)) +
  theme_bw()
```
